Efficient pedigree recording for fast population genetics simulation

### 2018-01-01 forwards_paper.tex
edit intro

However, it is thought that most genetic variation is selectively neutral (or nearly so).
By definition, the neutral alleles carried by individuals in a population
do not affect the population process.
For this reason, if one records the entire genealogical history of a population over the course of a simulation,
simply laying down neutral mutations on top of that history afterwards
is equivalent to having generated them during the simulation.
Precisely, we would need to know the genealogical tree relating all sampled individuals
at each position along the genome.
This \emph{population pedigree} is 
the complete history of parent-offspring relationships of an entire population
going back to a remote time including the genetic outcomes of each ancestral
meiosis.
The embellished pedigree contains all the information necessary
to construct the genealogical tree that relates each individual to every other
at each position on the genome,
i.e., the \emph{tree sequence} implemented in the coalescent simulator \msprime{}~\citep{kelleher2016efficient}.
Combined with ancestral genotypes and the origins of new mutations,
it also completely specifies the genomic sequence of any individual in the population at any time.
This is much much more than typically recorded in a forward simulation, however,
so further savings can be had by discarding all information irrelevant to the genetic history
of the extant population.
\jda{The space complexity result seemed like a result in the intro; and maybe didn't include some detail
	about assumed number of generations}

>>>>

However, it is thought that most genetic variation is selectively neutral (or nearly so).
By definition, the neutral alleles carried by individuals in a population
do not affect the population process.
For this reason, if one records the entire genealogical history of a population over the course of a simulation,
simply laying down neutral mutations on top of that history afterwards
is equivalent to having generated them during the simulation.
Precisely, we would need to know the genealogical tree relating all sampled individuals
at each position along the genome.
This is equivalent to knowing the \emph{population pedigree} --
the complete history of parent-offspring relationships of an entire population
going back to a remote time -- and the genetic outcomes of each ancestral
meiosis.
The embellished pedigree contains all the information necessary
to construct the genealogical tree that relates each individual to every other
at each position on the genome,
i.e., the \emph{tree sequence} implemented in the coalescent simulator \msprime{}~\citep{kelleher2016efficient}.
Combined with ancestral genotypes and the origins of new mutations,
it also completely specifies the genomic sequence of any individual in the population at any time.
This is much much more than typically recorded in a forward simulation, however,
so further savings can be had by discarding all information irrelevant to the genetic history
of the extant population.
\jda{The space complexity result seemed like a result in the intro; and maybe didn't include some detail
	about assumed number of generations}
